\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
fixed typos in 4.3
in sec 2

We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift
the equality $=$ operation to tuples in the standard way.

@@

For presentation purposes, we provide a sketch of a highly simplified language
for describing reducers. The language allows us to give examples of reducers and
to discuss our approach for checking their commutativity. Let $\Var$ be a set of
\emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
a~variable from $\Var$, a constant value, a call to the $\cur$ function that
reads and consumes an input value of the reducer, their combinations over basic
arithmetic operations, or a non-deterministically chosen integer value $*$. A
\emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of
commands, or an $out(v)$ statement that outputs the value of $v \in \Var$. A
\emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$ where $s_1,s_2,s_3
\in \Cmd$. According to our observation over hundreds  of reducer programs in
open repositories, reducer programs are almost always in this form. The
$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly for
each input element until the entire input list is consumed. An example of a
reducer is shown in Figure~\ref{fig:reducer_example}. In the paper, to simplify
the presentation, we assume that a reducer does never produce any output in the
loop body $s_2$. In the J-ReCoVer tool, an algorithm to deal with the output
inside the loop is implemented (as briefly mentioned at the end of
Section~\ref{sec:prover}).

>>>>

We use $[n,m]$ to denote the set of integers $\{k\mid n \leq k\leq m\}$ and lift
the equality predicate $=$ to tuples in the standard, component-wise, way.

@@

%For presentation purposes, we provide a sketch of a highly simplified language
%for describing reducers. 
%%
%The language allows us to give examples of reducers and
%to discuss our approach for checking their commutativity. 
%
To present our approach, we introduce a highly simplified language
for describing reducers. 
%
Let $\Var$ be a set of
\emph{integer variables}. An \emph{integer expression} in $\Exp$ can either be
a~variable from $\Var$, a constant value, a call to the $\cur$ function that
reads and consumes an input value of the reducer, a non-deterministically chosen integer value $*$, or a combination of integer expressions over basic
arithmetic operations. A
\emph{command} in $\Cmd$ can be an assignment, a branch statement, a sequence of
commands, or an $out(v)$ statement that outputs the value of $v \in \Var$. A
\emph{reducer program} is defined as $s_1;\rloop\{s_2\};s_3$ where $s_1,s_2,s_3
\in \Cmd$. According to our observation over hundreds  of reducer programs in
open repositories, reducer programs are almost always in this form. The
$\rloop\{s_2\}$ statement enters the loop body to execute $s_2$ repeatedly for
each input element until the entire input list is consumed. An example of a
reducer is shown in Figure~\ref{fig:reducer_example}. In the paper, to simplify
the presentation, we assume that a reducer does never produce any output in the
loop body $s_2$. In the J-ReCoVer tool, an algorithm to deal with the output
inside the loop is implemented (as briefly mentioned at the end of
Section~\ref{sec:prover}).
